%% Copyright 1998 Pepe Kubon
%%
%% `three.tex' --- 3rd chapter for thes-full.tex, thes-short-tex from
%%               the `csthesis' bundle
%%
%% You are allowed to distribute this file together with all files
%% mentioned in READ.ME.
%%
%% You are not allowed to modify its contents.
%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Chapter 3   
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{User Stories}
The chapter will describe user stories on the native Social Needle site. The next chapter, Native-side Functionalities, will be based on this chapter. 

\section{Native-side}
\subsection{Instructors}
\begin{enumerate}
	\item \textbf{As an instructor, I want to make administrative announcements} \\
	The instructor logs in to the native site, goes to the course page. The instructor chooses to create a new post, fills in title, content, and tags the post as ``Announcement''. Simultaneously, the post will also be pushed to Facebook Page (created for the course) and the Twitter account (also created for the course). Students will be able to see the announcement from all three platforms.  
	
	\item \textbf{As an instructor, I want to answer questions posted by students:} \\
	The instructor sees a interesting question posted by a student. The instructor comments on the post and answers the question. His/Her answer will be pushed to Facebook Page and Twitter.
	 
	\item \textbf{As an instructor, I want to follow a post that interests me:} \\
	The instructor sees an interesting post. The instructor goes to the post viewing page and adds the post to one of his/her collections. Thus, the instructor will get all updates on the post in his/her news feeds.
\end{enumerate}

\subsection{Students}
\begin{enumerate}
	\item \textbf{As a student, I want to enrol in a course on Social Needle:} \\
	The student logs in to the native site and follows the course. 
	
	\item\textbf{ As a student, I want to follow announcements made by instructor:} \\
	The student goes to the tags/collections page. The student sees the related announcement tag/collection for the course announcements, and follows the tags/collections. The student will get subsequent updates on topics on that course. 
	
	\item \textbf{As a student, I want to post my questions on Social Needle:} \\
	The student proceeds to create a new post. The student enters his/her questions, tags the question with appropriate tags and creates the post. It will appears in the news feeds of the students and instructors who follow the tags. In the meantime, the content of the post will be pushed to Facebook Page and Twitter, so that users can see the question from all three platforms.
	
	\item \textbf{As a student, I want to create a collection of the posts that interested me:} \\
	The student sees a interesting post and decide to keep it in his/her collection. In another words, the student thinks he/she may want to revisit the post later or just want to archive interesting topics. The student can create a collection in the post viewing page and add the current post to the collection. The student can also add the post to a existing collection by selecting the name of the collection. 
	
	\item \textbf{As a student, I want to follow a question:} \\
	The student sees an interesting post on the native site. The student goes to the post page and adds the post to one of his/her collections. Then the student will get updates on the posts in his/her news feeds.
	
	\item \textbf{As a student, I want to answer the questions posted by my classmates:} \\
	The student sees a interesting post in his/her news feeds. The student comments on the post and answers the question. All other students and instructors who follow this post will get updates about the new comments. Simultaneously, the answer will be pushed to Facebook Page and Twitter. On Twitter, the answer will be sent to all users who have retweeted or replied to the original post. 

\end{enumerate}

\section{Facebook-side}

\begin{enumerate}
	\item \textbf{As an instructor, I want to create a course Facebook Page called ``CMPT-XXX'':} \\
	The instructor can simply create a Page by following the Page creation procedure.
	
	\item \textbf{As an instructor, I want to give Social Needle permission to manage my course Facebook Page:} \\
	The instructor goes to the course web page on the native website of Social Needle. The instructor clicks ``Connect to Facebook'' button on the web page and follows Facebook's authentication procedure to grant permission for out application to manage the Facebook Page.
	
	\item \textbf{As a student, I want to give Social Needle permission to post on course Facebook Page using my account:} \\
	 The student logins to the native website of Social Needle and goes to his/her account settings. The student clicks the ``Connect to Facebook'' button on the settings web page and follows Facebook's authentication procedure to grant permission for our application to post on on course Page's wall using his/her account.
	
	\item \textbf{As an instructor/student, I want to post text on the Facebook Page's wall and synchronize it to native website as well as other clients (e.g. Twitter):} \\
	The instructor/student logins to Facebook and goes to the course Facebook Page ``CMPT-XXX''. The instructor/student posts text as Status. After posting on ``CMPT-XXX'' Facebook Page, the post will appear on our native website as well as other clients (e.g. Twitter).
	
	\item \textbf{As an instructor/student, I want to reply to post on the Facebook Page. The reply will be synchronized to native website as well as other clients (e.g. Twitter):} \\
	The instructor/student logins to Facebook and goes to the course Facebook Page ``CMPT-XXX''. Under the Status, he/she clicks the ``Comment'' button and replies to the Status. After replying on ``CMPTXXX'', the comment will appear on our native website as well as other clients (e.g. Twitter).
\end{enumerate}

\section{Twitter-side}


\subsection{Connect A Twitter Timeline to Course Page}

An instructor of a course is able to connect a Twitter account to a
course page on native site. This Twitter account will be used as the
timeline to update topics related to the course.

In order to connect the Twitter account with a course page on native
site, the instructor will need to register a twitter account and
Social Needle account first. Then she needs to login to Social Needle
native site, where she can create a course page and specify a twitter
account to which she hopes to connect the course page.

\subsection{View Existing Topics}

For the students who have Twitter accounts to view topics of a
specific course, they need to follow the Twitter account that has been
connected to a course page. Once this is done, they will be able to
see on their own Twitter timeline the topics posted a the course
page. View course-related topics is done in exactly the same way as
they would anticipate any other Tweets from Twitter account they
follow. It is thus supposed to be easy for the Twitter users to use.

\subsection{Post A New Topic}

After they follower the Twitter account that is connected to a course
page, the users can post a topic by posting a Tweet that mentions the
Twitter account for course. This Tweet must starts with
\textit{@twitter\_account}, where \textit{twitter\_account} is the
name of the Twitter account that is connected to the page. This Tweet
will be saved into Social Needle's native site, and the users from the
native site will see the topic.

When a user creates the Tweet that mention a Twitter account, the
metion can be seen in the Social Needle native site, but it cannot be
seen by most other users who follower the same Twitter account,
because this Tweet is only seen by Twitter users who follow both the
mentioning account and the mentioned account. In order for all the
course followers to see the post, the Social Needle site instructs the
Twitter account for the course to post a Tweet that contains the
information of the original Tweet, which will then be seen in the
followers timeline. In this way, all the course followers will be able
to see the post.

Users can also post topics from Social Needle native site or from
Facebook, and those topics will be eventually posted on the Twitter
course page as Tweets in the same way as the topics originated in
Twitter.

\subsection{Share Topics}

An important feature of social networking sites is sharing of
information. We also allow Twitter users to share interesting posts
with their friends. This encourages more people to participate in
discussions of topics. 

To share a topic, a users can simply click on the ``retweet'' button of a
topic posted by the Twitter page for course. This retweet will be seen
by her followers, who can in turn retweet the retweet. 


\subsection{Reply to A Topic}

Once Twitter users see a topic in their timeline, they can reply to
the topic by using the ``reply'' button below the topic.  The reply
will be saved to Social Needle native site and be seen by Social
Needle users. The Twitter users can see the reply by clicking on the
Tweet being replied to. It is important to notice that users can reply
to retweets of the topic, and those replies will have exactly the same
effect as replies to the original topic, which can be seen by native
site users and Twitter users.
